Drivers of Phytoplankton Community Variability in the Cariaco Basin, Venezuela

### 2024-09-26 agujournaltemplate.tex

\begin{keypoints}
\item The phytoplankton community data identified by microscopy from the CARIACO Time Series between 1996 and 2016 shows two separate clusters characterized by high and low upwelling regimes respectively.
\item Despite the differing physical regimes and large shifts between functional groups, there is no significant difference in diversity metrics between the two clusters. Overall the data shows a positive relationship between Richness and Biomass, Productivity as well as Resource Use Efficiency.
\item A gradient forest analysis of the community data reveals that the strongest predictor of shifts within the community is the AMO index, which points to a strong impact of large scale climatic oscillations in the tropical coastal ecosystem.
\end{keypoints}

@@

\section*{Plain Language Summary}
Enter your Plain Language Summary here or delete this section.
Here are instructions on writing a Plain Language Summary: 
https://www.agu.org/Share-and-Advocate/Share/Community/Plain-language-summary

@@

\begin{figure}
\noindent\includegraphics[width=\textwidth]{fig/GF_output_plot2.pdf}
\caption{caption}
\end{figure}

@@

% \section*{Open Research Section}
%This section MUST contain a statement that describes where the data supporting the conclusions can be obtained. Data cannot be listed as ''Available from authors'' or stored solely in supporting information. Citations to archived data should be included in your reference list. Wiley will publish it as a separate section on the paper’s page. Examples and complete information are here:
%https://www.agu.org/Publish with AGU/Publish/Author Resources/Data for Authors

@@

\acknowledgments
Enter acknowledgments here. This section is to acknowledge funding, thank colleagues, enter any secondary affiliations, and so on.

>>>>

\begin{keypoints}
\item The phytoplankton community data identified by microscopy from the CARIACO Time Series between 1996 and 2016 shows two separate clusters characterized by high and low upwelling regimes respectively.
\item Despite the differing physical regimes and large shifts between functional groups, there is no significant difference in diversity metrics between the two clusters. Overall the data shows a positive relationship between Richness and Biomass, Productivity as well as Resource Use Efficiency.
\item A gradient forest analysis of the community data reveals that the strongest predictor of shifts within the community is the AMO index with a time lag of 4 months, which points to a strong impact of large scale climatic oscillations in the tropical coastal ecosystem.
\end{keypoints}

@@

%1
%\section*{Plain Language Summary}
%Enter your Plain Language Summary here or delete this section.
%Here are instructions on writing a Plain Language Summary: 
%https://www.agu.org/Share-and-Advocate/Share/Community/Plain-language-summary

@@

\begin{figure}
\noindent\includegraphics[width=\textwidth]{fig/GF_output_plot3.pdf}
\caption{caption}
\end{figure}

@@

%!
% \section*{Open Research Section}
%This section MUST contain a statement that describes where the data supporting the conclusions can be obtained. Data cannot be listed as ''Available from authors'' or stored solely in supporting information. Citations to archived data should be included in your reference list. Wiley will publish it as a separate section on the paper’s page. Examples and complete information are here:
%https://www.agu.org/Publish with AGU/Publish/Author Resources/Data for Authors

@@

%!
%\acknowledgments
%Enter acknowledgments here. This section is to acknowledge funding, thank colleagues, enter any secondary affiliations, and so on.
